A Visibility-Based Combinatorial Data Structure for Mobile Robots in Polygons

### 2018-05-17 final_paper/paper.tex
contraction map stuff

\section{Bounce Visibility Diagram}
We will now define the central structure for this paper, the
\textit{Bounce Visibility Diagram} for polygon $P$. We will first insert all new
vertices from the partial local sequence for all vertices into the
polygon $P$, creating the new polygon $P'$ with $m$ vertices. Note that $P'$ is
no longer a polygon in general position.

@@

Let $n = 4t+2$, where $t$ is a positive integer. We design a polygon with $r = 2t$ reflex vertices. The polygon is symmetric with respect to its medium horizontal line. In the top half, the reflex vertices are uniformly located on a circle and thus they are visible to each other; the convex vertices are chosen so that they are outside the circle and the line through an edge will not intersect other edges. Each reflex vertices will have at least $t-1$ new vertices in its partial local sequence. All vertices in the top half can see each vertex in the bottom half and vice versa. So there will be $2t(t-1)+n$ vertices in the polygon after we insert all new vertices in the partial local sequence for all reflex vertices. Each of them can see at least $t(t-1)+n/2$ other vertices. The final complexity for the bounce visibility diagram is $\Theta ((2t(t-1)+n)(t(t-1)+n/2)) = \Theta (t^4) = \Theta(n^4)$. Fig~\ref{fig:chestnut} shows the polygons for $t = 4$ and $t=6$ with all the vertices in the partial local sequences.
% show the diagram to edge 
% show the fix bounce
% show the periodic behavior
% show the gap navigation
% show we could find equivalent class on theta
% \begin{itemize}
% \item Big O complexity of construction, and size of resulting graph

@@

@@

Given an environment $P$, a start set of possible robot positions along the
environment boundary $S$, and a goal set $G$, determine a strategy $\pi$ which
will be guaranteed to take the robot from any point in $S$ to a point in $G$.

If the start set $S$ is such that it lies entirely within one of the equivalence
classes of the data structure, a navigation query is simple - the start set in
the graph is a single node, and the query is solved by a shortest path from this
node to the nodes representing the goal set. The shortest path will correspond
to the navigation strategy with the fewest number of bounces.

@@

If the start set $S$ lies in more than node of the graph, things get a bit
trickier.

Their approach can be replicated with the current work by the following
procedure: take the {\color{red}NAME} graph, and remove edges which represent unsafe actions.
Also need to add a corner finding strategy (how do we know when we've found the
corner?).

\subsection{Patrolling}

>>>>

\section{Bounce Visibility Diagram \label{bvd_def}}
We will now define the central structure for this paper, the
\textit{Bounce Visibility Diagram} for polygon $P$. We will first insert all new
vertices from the partial local sequence for all vertices into the
polygon $P$, creating the new polygon $P'$ with $m$ vertices. Note that $P'$ is
no longer a polygon in general position.

@@

Let $n = 4t+2$, where $t$ is a positive integer. We design a polygon with
$r = 2t$ reflex vertices. The polygon is symmetric with respect to its medium
horizontal line. In the top half, the reflex vertices are uniformly located on a
circle and thus they are visible to each other; the convex vertices are chosen
so that they are outside the circle and the line through an edge will not
intersect other edges. Each reflex vertices will have at least $t-1$ new
vertices in its partial local sequence. All vertices in the top half can see
each vertex in the bottom half and vice versa. So there will be $2t(t-1)+n$
vertices in the polygon after we insert all new vertices in the partial local
sequence for all reflex vertices. Each of them can see at least $t(t-1)+n/2$
other vertices. The final complexity for the bounce visibility diagram is
$\Theta ((2t(t-1)+n)(t(t-1)+n/2)) = \Theta (t^4) = \Theta(n^4)$.
Fig \ref{fig:chestnut} shows the polygons for $t = 4$ and $t=6$ with all the
vertices in the partial local sequences. % show the diagram to edge

% show the fix bounce
% show the periodic behavior
% show the gap navigation
% show we could find equivalent class on theta
% \begin{itemize}
% \item Big O complexity of construction, and size of resulting graph

@@

Information spaces \cite{tovar2005information} are a useful formalism for
reasoning about the information available to a robot as a result of its sensor
and action history. From the \emph{history information space} (the space of all
sensor/action histories), we can define mappings to other, more useful spaces.

Here we will show that the bounce visibility diagram can induce a useful
information space for many mobile robot tasks, and can be augmented with
information from the geometric properties of actuators and sensors.

We will construct $G_{BVD}$, a graph where nodes are segments in the decomposed
environment $P'$ constructed in Section \ref{bvd_def}.

We then define edges in this graph to be transitions between these segments, based on the bounce laws and
required to transition between them. First, we observe that any two segments in
$P'$ that are visible at all are visible along their entire lengths. Thus, we
there exists a function $f$ which maps a point $s \in v_i
v_{i+1}$ to a point $f(s) \in v_j v_{j+1}$ under a bounce at angle $\theta$ from
the normal on edge $v_i v_{i+1}$, for all valid ranges of $s$, $f(s)$, and
$\theta$.

Rather than use $f$ directly, we take a nondeterministic approach and define a
directed transition between edges $v_i v_{i+1}$ and $v_j v_{j+1}$ if it is
possible to reach edge $v_j v_{j+1}$ from edge $v_i v_{i+1}$ under any bounce.
We label the edge with the range of bounce angles, $\theta_{min} < \theta <
\theta_{max}$, under which this is possible. See Figure \ref{fig:bounce_range} for
the geometric definitions of $\theta_{max}$ and $\theta_{min}$.

\begin{figure}
    \includegraphics[width=0.8\linewidth]{images/bouncerange.png}
    \centering
    \caption{Definitions of $\theta_{max}$ and $\theta_{min}$. Can be computed
by rotating the source edge to the x axis without loss of generality.}\label{fig:bounce_range}
    \centering
\end{figure}

We can also add information to the edges in $G_{BVD}$ indicating whether the
mapping from one edge to another is a \emph{contraction mapping}: a transition
which will bring two separate points in the domain closer together in the range,
a useful property for reducing state uncertainty and engineering limit cycles,
as will be discussed in Section \ref{patrol}.

The necessary condition for $f$ to be a contraction mapping is:

\begin{equation*}
|f(x) - f(y)| \leq c |x-y|
\end{equation*}

such that $0 \leq c < 1$.

From Figure \ref{fig:cont_map}, we can see that

\begin{equation*}
|f(x) - f(y)| = \frac{\sin(\theta - \phi)}{\sin(\pi-\theta)} |x-y|
\end{equation*}

from the law of sines, where $\phi$ is the angle between the two edges if they
are extended to their intersection point. If the edges are parallel, a
contraction map is not possible (points will maintain their distance, not shrink
closer together). Thus, whenever $\frac{\sin(\theta - \phi)}{\sin(\pi-\theta)}
< 1$, $f$ is a contraction map, and the edge from $v_i v_{i+1}$ to $v_j
v_{j+1}$ can be labelled as such, with the range of $\theta$ which makes this
condition true.

\begin{figure}
    \includegraphics[width=0.8\linewidth]{images/contraction_map_cond.png}
    \centering
    \caption{\label{fig:cont_map}}
    \centering
\end{figure}

@@

\begin{quotation}
Given an environment $P$, a start set of possible robot positions along the
environment boundary $S$, and a goal set $G$, determine a strategy $\pi$ which
will be guaranteed to take the robot from any point in $S$ to a point in $G$.
\end{quotation}

If the start set $S$ is such that it is equal to one of the equivalence
classes of the data structure, a navigation query is simple - the start set in
the graph is a single node, and the query is solved by a shortest path from this
node to the nodes representing the goal set. The shortest path will correspond
to the navigation strategy with the fewest number of bounces.

@@

If the start set $S$ lies in more than node of the graph, things get a bit
trickier. We need to guarantee all-path reachability for a set of start nodes in
a graph. There are also complications if the user-specified start set does not
exactly overlap the equivalence classes formed by the decomposition in Section
\ref{bvd_def}. For now, we can only guarantee navigation from one equivalence
class (segment along the new polygon $P'$) to another.

\subsection{Patrolling \label{patrol}}
